### 2025-03-18 paper/manuscript.qmd
added paradigm ppt

<!-- Study 1  -->

<!-- Study 2 -->

>>>>

```{r}
#| label: setup
#| include: false
library(conflicted)
library(tidyverse)
library(flextable)
library(ftExtra)
library(officer)
library(knitr)

conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
# options and parameters
options(digits = 3)

knitr::opts_chunk$set(
    collapse = TRUE,
    dpi = 450,
    fig.width = see::golden_ratio(9),
    fig.height = 9,
    fig.path = "images/"
)

cache <- TRUE
```

# Study 1

## Methods

**Participants**

**Materials**

**Procedure**

```{r}
#| message: false
#| warning: false

knitr::include_graphics("images/Paradigm.png")
```

**Ethics**

**Data Analysis**

# Study 2

## Methods

**Participants**

**Materials**

**Procedure**

**Ethics**

**Data Analysis**
